Response to reviewers

### 2024-11-28 Manuscript/ecography_reponse_letter.tex
reviewer 1 item 2 done

\textit{To understand the ability of each metric to capture a mechanism of interest, we compared their scores relative to the same metric scores of a null mechanism.
To ease interpretation of the results across a range of metrics with different orders of magnitudes of outputs and different random simulations, we first calculated the difference between the stressor of interest and the null stressor (e.g. $metric_{stressor20\%} - metric_{null20\%}$).
We then scaled these differences to be relative to the highest relative differences between all the simulations for that one metric and stressor (across the 4 levels of removal - 20\%, 40\%, etc.)
This resulted in each metric being scaled between $-1$ and $1$ where a negative difference can be interpreted as the random removal of elements leading to a higher metric score; a positive difference as the focal removal of elements (i.e. approximating equalisation, facilitation, filtering and competition) leading to a higher metric score; and a difference near $0$ meaning both the null stressor and the focal stressor having a similar effect on the metric score (Figs \ref{Fig:simulations}, \ref{Fig:simulation_results} and \ref{Fig:empirical_results}).
We interpret this last scenario as the metric score being unable to clearly distinguish between a random removal of elements and a non random one.
To assess these poor performances, we compared the distributions of the $171$ scores for each metric with each reduction level for each non-null stressor to the null stressor using pairwise t-tests.
The results of these tests are displayed in figure \ref{Fig:simulation_results} (for the non-null stressor, grey distributions are not clearly distinguishable from the null stressor).}
Lines 273-291.

% \textit{Finally, we measured the effect of the different strengths of the stressors (i.e.~removing 20\textbackslash\%, 40\textbackslash\%, 60\textbackslash\% and 80\textbackslash\% the data) by fitting a linear regression using the scaled metric difference to null score as a function of the amount of data removed.}
%  \textit{For each of these models, we reported the variance explained by the model (adjusted \(R^2\)) in the supplementary tables \(1\) to \(3\) and whether the slope was clearly distinguishable from \(0\) (Figure \textbackslash ref\{Fig:simulation\_results\}).}
%  \textit{This allowed us to see if there was any predictable linearity in the metric scores.}
%  \textit{In other words testing whether the metric scores relative to null removals where linearly scaling with the amount of data removed.}
%  Lines @@@

% We have also added a panel to figure 1 helping the reader to easily interpret our results in figures 2 and 3.

>>>>

\textit{To understand the ability of each metric to capture a mechanism of interest, we compared their scores relative to the same metric scores of a null mechanism.
To ease interpretation of the results across a range of metrics with different orders of magnitudes of outputs and different random simulations, we first calculated the difference between the stressor of interest and the null stressor (e.g. $metric_{stressor20\%} - metric_{null20\%}$).
We then scaled these differences to be relative to the highest relative differences between all the simulations for that one metric and stressor (across the 4 levels of removal - 20\%, 40\%, etc.)
This resulted in each metric being scaled between $-1$ and $1$ where a negative difference can be interpreted as the random removal of elements leading to a higher metric score; a positive difference as the focal removal of elements (i.e. approximating equalisation, facilitation, filtering and competition) leading to a higher metric score; and a difference near $0$ meaning both the null stressor and the focal stressor having a similar effect on the metric score (Figs 1, 2 and 3).
We interpret this last scenario as the metric score being unable to clearly distinguish between a random removal of elements and a non random one.
To assess these poor performances, we compared the distributions of the $171$ scores for each metric with each reduction level for each non-null stressor to the null stressor using pairwise t-tests.
The results of these tests are displayed in figure 2 (for the non-null stressor, grey distributions are not clearly distinguishable from the null stressor).}
Lines 273-291.

\textit{Finally, we measured the effect of the different strengths of the stressors (i.e. removing 20\%, 40\%, 60\% and 80\% the data) by fitting a linear regression using the scaled metric difference to the null score as a function of the amount of data removed
For each of these models, we reported the variance explained by the model (adjusted $R^2$) in the supplementary tables $2$ to $5$ and whether the slope was clearly distinguishable from $0$ (Figure 2b; \textit{sensu} Dushoff et al. 2019).
This allowed us to see if there was any predictable linearity in the metric scores.
In other words testing whether the metric scores relative to null removals where linearly scaling with the amount of data removed.}
Lines 292-299.

We have also added a panel to figure 1 helping the reader to easily interpret our results in figures 2 and 3.

### 2024-11-28 Manuscript/main_ecography_R1.tex
reviewer 1 item 2 done

Finally, we measured the effect of the different strengths of the stressors (i.e. removing 20\%, 40\%, 60\% and 80\% the data) by fitting a linear regression using the scaled metric difference to the null score as a function of the amount of data removed.
For each of these models, we reported the model fit (adjusted $R^2$) in the supplementary tables $1$ to $3$ and whether the slope was clearly distinguishable from $0$ (Figure \ref{Fig:simulation_results}; \textit{sensu} \cite{dushoff2019can}).
This allowed us to see if there was any predictable linearity in the metric scores.
In other words testing whether the metric scores relative to null removals were linearly scaling with the amount of data removed.

>>>>

Finally, we measured the effect of the different strengths of the stressors (i.e. removing 20\%, 40\%, 60\% and 80\% the data) by fitting a linear regression using the scaled metric difference to the null score as a function of the amount of data removed
For each of these models, we reported the variance explained by the model (adjusted $R^2$) in the supplementary tables $2$ to $5$ and whether the slope was clearly distinguishable from $0$ (Figure \ref{Fig:simulation_results}; \textit{sensu} \citealt{dushoff2019can}).
This allowed us to see if there was any predictable linearity in the metric scores.
In other words testing whether the metric scores relative to null removals where linearly scaling with the amount of data removed.
